--- 
title: "Retail Metrics in R"
author: "Christopher Ried"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "The following book using R to expound on the influences and challenges on retail metrics"
---

# Prerequisites

The following book takes into consideration that you have some familiarity with R and have had some sort of experience in retail. However this has been written to be practical; rather than very theoretical in order for the practicing novice to pick up and complete their own analysis of retail data.

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
