--- 
title: "Retail Metrics in R"
author: "Christopher Ried"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "The following book using R to expound on the influences and challenges on retail metrics"
---

# Prerequisites

The following book takes into consideration that you have:

* Interest in learning new things 
* familiarity with R 
* Domain knowledge in retail


However this has been written to be practical; rather than  theoretical so that the practicing novice can pick this up and complete their own analysis of retail data.

```{r echo=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

## Purpose 
The following book gives the retail data analyst or scientist the core skillset in order to be able to pivot. 

The disruption of retail continues to speed up creating an environment that is feared by the largest of companies and tends to be run by a few at the top (i.e. Amazon, Walmart). Thus there are a few advantages one needs to take in this climate. Data and speed. 

### Data
There are so many ways to monitor data within a store. Anything from simple traffic counters, to the complexity of an Amazon Go store. Thus it is imperitive to start collecting as much data as you can. It is not in your interest to try to collect some; rather collect more than you can get. Your future self will be quite thankful. 

### Speed 
And as retail becomes more competitive, it is important to quickly pivot and be able to make change based upon the climate of your users. They will want you to provide them experiences that are unique and special. It can make and break them. Thu speed in data also is important. It needs to be **accessable** to everyone who can use it; and you will need to **talent** to be able to address these analysis quicker than the rest of them.

<!--chapter:end:01-Introduction.Rmd-->

# Retail Overview 

Retail metrics... I suppose it is something you have to be passionate to write about. Or really miserable to try to pinpoint the common methodologies by which one is able to manage a store. However it is important to understand the way it works in ordeer to be able to give one's best attention to the work. 


* Total Gross Sales $S_G$ / Gross Sales $S_g$
* Returns $S_r$


## Total Net Sales 
$$
S_{NET} = \sum{S_{g}-S_{r}}
$$

One of the fundamental metrics to navigate the success and growth of any organization is the Net Sales. It is the overall amount of Revenue metric. 

## Year over Year Growth 
$$
S_{YOY} = \frac{S_{net_{TY}}-S_{net_{LY}}}{S_{net_{LY}}}
$$

YOY comparision of sales shed light in the growth of the company. Some of these factors include: 

* **Product Mix**: there is alot of science in this, but having the right product for your store is extremely important. But having even more "right" product for your customers will increase their frequency to buy. On the flip side, you will see a negative growth if your customers do not find the right product. This will eventually frustrate them to not return, and its only new customers that will bring back more people. 

* **New Customers**: Especially when the store is brand new, it can take some time for your customers to find your store. But as the word spreads about the store, they find themselves to at least check your store. 

* **Repeat Customers**: Not all, but a percentage of customers, if they find value in coming again, they will continue to come to your same store. That way the growth continues to be level giving new repeat customers the basis to grow. 


## Return Rate
$$
\%\ Return\ Rate = \frac{S_g}{S_r}
$$

The return rate is used as a measure of the product that is returned to the store by the customer in comparision to what has been sold out of the same store. This metric, as it changes, can indicate a number of influencing factors such as follows

* **Quality of product**: If the product source has changed; or the material of the product has changed and has left the customer less satisified with the product, generally you will see the return rate increase. 
* **shrinkage of product**: As one of the metrics that can be used to signal deviant behavior by a single store or a particular individual when compared to the rest of the store.
* **demographic shifts**: Less frequent, but possible it can be found that as more individuals move out of an area; there might be a change in the philosophy and ethics in returning items to a particular store. 


## Average Units Per Transactions 
$$
Average\ Transactions = \frac{Units\ Sold}{Transactions}
$$
The average transaction size is indicative of how many units the average customer buys. This metric is very similar to the   The increase or decrease of the average transactions depends

* **Quality of Product**


## Weeks of Supply 
$$
WOS = \frac{Store\ Inventory}{Week\ Gross\ Sales}
$$
We can have WOS which will give us the ability to monitor the amount of product inside a store and how lng it might take to sell through the entire product. 

## Basket Size
$$
Basket\ Size = \frac{Gross\ Sales}{Units\ Sold}
$$


## Markdown Percent
$$
Markdown = 1 - (\frac{Gross\ Sale}{Total\ Retail\ Value} )
$$


## Sell-Thru 
Following sell thru rate shows or determines how much inventory has been sold. This is a measure of how much of the stock is left over. 
$$
Sell\ Thru=\frac{Current_\ Inventory_{date}}{Sales_{date}} 
$$

## Inventory Turns 

<!--chapter:end:02-RetailOverview.Rmd-->

# Forecasting

Again this could be an entire book just on forecasting but the following chapter will run down an example in which a forecast is made to better advice the outcomes of a particular buy. 

## Store Sales
In order to project the years sales; there are a 

## Labor Demand

<!--chapter:end:03-Forecasting.Rmd-->

# Simulations

Being able to take the information that we already know and use it to determine alternative outcomes in an unknown circumstance. 


## Monte Carlo 
This recursive algorithm has been around for some time now; but it continues to be the core of many simulatory methodologies. 

## Gaussian Mixed Models (GMM)
The following mixture model takes into consideration... 
> TODO: I need to use the following: http://tinyheero.github.io/2016/01/03/gmm-em.html

<!--chapter:end:04-Simulations.Rmd-->

# Operational Metrics

From the financial point of view; this is one of the most important driving mechanisms to be able to manage the expenses of a store. It gives the decision make the ability to better their overall profit margins within the stores.  

<!--chapter:end:05-OperationalMetrics.Rmd-->

# Product Allocation 

Product allocation essentially tries to fulfill the need of a certain product in a store. This can be based off a number of different drivers; however some of the most important are WOS. 

$$
WOS = \frac{C_i}{\bar{x}_{ws}}
$$

* $C_i$ - Current Inventory 
* $\bar{x}_ws$ - Weekly Sales

<!--chapter:end:06-ProductAllocation.Rmd-->

# Regression Analysis 

It is important to understand how multiple factors (or variables) relate to one another within a dataset. 

Take for example the following marketing dataset. 

```{r}

```


<!--chapter:end:07-Regression.Rmd-->


# Outlier Analysis

Specifically from a Loss Pervention perspective; using different forms of outlier analysis will help understand deviant behavior and helps identify. 



## Z-Score 




## Bayesian Outlier Analysis 

<!--chapter:end:08-Outliers.Rmd-->

# Classification 

There are many uses of classification in the retail space. Some of these can be difficult to understand as they might have unintended effects upon each other. The following methods will help identify these issues. 


## Customer Segmentation 

## Product Types

## Complementary Products 

<!--chapter:end:09-Classification.Rmd-->

# Pricing Optimization

Pricing is important to both the Seller and Buyer; creating a situation in which you try to find the maximum benefit for both the user and seller. 

## Demand Curves
Finding an optimum can be done by running a couple simple AB Tests to be able to find the Minimum / Maximum optimzation. 

<!--chapter:end:10-PricingOptimization.Rmd-->

# Final Words

Thank you for making it to the end of this book. It has been a fun adventure trying to come up with a simple but comprehensive analysis of retail metrics. 

<!--chapter:end:11-Summary.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:references.Rmd-->

